\Section{outline}{Outline}
\begin{itemize}

\item Motivation argument:
  \begin{itemize}
    \item Logical entailment is high-precision, but often hopelessly low recall.
          Find some citations for this.
    \item Lexical classification is high-recall, and often a surprisingly good baseline
          for a number of tasks.
          Steal Bill's citations for this in RTE.
          \tred{Is ``lexical classification'' the word to use here?}
    \item But, these lexical classifiers often make embarrassing mistakes.
          For example, omitting a `not' in one sentence.
    \item Furthermore, these classifiers have a narrow view of the corpus.
  \end{itemize}

\item System description: We build a system which
  \begin{enumerate}
    \item Will search an arbitrarily large corpus for support or contradiction of
          a fact.
    \item Will do this search over a range of common entailment rules: natural
          logic + relational entailment + meronymy.
    \item Will back off to a soft lexical classifier if the search fails.
    \item BUT, which uses the information from the search to prevent the
          classifier from making embarrassing errors.
  \end{enumerate}

\item Sales pitch:
  The fact that natural logic operates directly on natural language allows us
  to both (1) do precise fact-finding over a large knowledge base using a
  wide range of common inference rules, and (2) directly provide signals to
  a standard IR + classifier approach when no fact is found.
\end{itemize}

\Subsection{examples}{Example Bank}
Some examples from the training set that motivate why this is a good idea to begin
with.

\begin{itemize}
\item \textbf{Explicit contradiction detection.} 
      The following is the highest classified
      entailment pair by the lexical classifier, but can be marked as a 
      contradiction: \\
  P: \w{Eating candy for diner [sic] is an example of a poor health habit.} \\
  H: \w{eating candy is an example of a good health habit.}

\item \textbf{Suggestive contradiction detection.} 
      If we ever match nearly every keyword on a negative state, consider the conclusion
      false:
  P: \w{The shortest number of daylight hours in New York State occurs during December.} \\
  H: \w{In New York State, the longest period of daylight occurs during December.}
\end{itemize}

\newpage
